---
output: pdf_document
params:
  data: data
  geo_labels: geo_labels
  dashboard_structure_indicator_data: dashboard_structure_indicator_data
  colors_palette: colors_palette
  bar_chart_colors_palette: bar_chart_colors_palette
title: "`r params$dashboard_structure_indicator_data$title[1]`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
# Read the parameters
data <- params$data
geo_labels <- params$geo_labels
dashboard_structure_indicator_data <- params$dashboard_structure_indicator_data
colors_palette <- params$colors_palette
bar_chart_colors_palette <- params$bar_chart_colors_palette

# latex has only three header levels, so I have to manually change from level 4 to 3
description <- gsub("####", "###", dashboard_structure_indicator_data$description[1])
```


`r description`


`r if (dashboard_structure_indicator_data$timeline[1]) {"## Time series"}`

```{r render plots, include=FALSE, eval=dashboard_structure_indicator_data$timeline[1]}
# Create variable which stores all subpages outputs
plots_out = NULL
  
# Set knitr options to allow duplicate labels (needed for the subpages)
options(knitr.duplicate.label = 'allow')
  
# Create temporary environment which we use for knitting plot.RMD 
plots_subpage_env <- new.env()
for(i in 1:nrow(dashboard_structure_indicator_data)) {
  # Generate the plot and save it as .png file to include it in the report
  timeline_fig <- generate_chart("timeline", data, geo_labels, colors_palette,
                                 dashboard_structure_indicator_data[i,]$timeline_ind, NULL,
                                 dashboard_structure_indicator_data[i,]$graph_title,
                                 dashboard_structure_indicator_data[i,]$timeline_subtitle,
                                 ".1f", TRUE)
  filename <- paste0("timeline_temp_", i, ".png")
  plotly::save_image(timeline_fig$fig, filename)
    
  # Assign plot to plots_subpage_env
  assign("filename", filename, plots_subpage_env)
    
  # Knit plot.RMD using the plots_subpage_env and add result to out vector
  plots_out = c(plots_out, knitr::knit_child('plot.RMD', envir = plots_subpage_env))
}
```

`r if (dashboard_structure_indicator_data$timeline[1]) {paste(knitr::knit_child(text = plots_out), collapse = '')}`


`r if (dashboard_structure_indicator_data$comp_barchart[1]) {"## Cross comparisons"}`

```{r render plots, include=FALSE, eval=dashboard_structure_indicator_data$comp_barchart[1]}
# Create variable which stores all subpages outputs
plots_out = NULL
  
# Set knitr options to allow duplicate labels (needed for the subpages)
options(knitr.duplicate.label = 'allow')
  
# Create temporary environment which we use for knitting plot.RMD 
plots_subpage_env <- new.env()
for(i in 1:nrow(dashboard_structure_indicator_data)) {
  # Generate the plot and save it as .png file to include it in the report
  bar_fig <- generate_chart("cross_country", data, geo_labels, bar_chart_colors_palette,
                            dashboard_structure_indicator_data[i,]$comp_barchart_ind, NULL,
                            dashboard_structure_indicator_data[i,]$graph_title,
                            dashboard_structure_indicator_data[i,]$comp_barchart_subtitle,
                            ".1f")
  filename <- paste0("bar_temp_", i, ".png")
  plotly::save_image(bar_fig$fig, filename)
    
  # Assign plot to plots_subpage_env
  assign("filename", filename, plots_subpage_env)
    
  # Knit plot.RMD using the plots_subpage_env and add result to out vector
  plots_out = c(plots_out, knitr::knit_child('plot.RMD', envir = plots_subpage_env))
}
```

`r if (dashboard_structure_indicator_data$comp_barchart[1]) {paste(knitr::knit_child(text = plots_out), collapse = '')}`


`r if (dashboard_structure_indicator_data$point_linechart[1]) {"## Point line chart plot"}`

```{r render plots, include=FALSE, eval=dashboard_structure_indicator_data$point_linechart[1]}
# Create variable which stores all subpages outputs
plots_out = NULL
  
# Set knitr options to allow duplicate labels (needed for the subpages)
options(knitr.duplicate.label = 'allow')
  
# Create temporary environment which we use for knitting plot.RMD 
plots_subpage_env <- new.env()
for(i in 1:nrow(dashboard_structure_indicator_data)) {
  # Generate the plot and save it as .png file to include it in the report
  ecoin_fig <- generate_chart("ecoin", data,
                              dashboard_structure_indicator_data[i,]$point_linechart_dim,
                              colors_palette,
                              dashboard_structure_indicator_data[i,]$point_linechart_ind_point_linechart,
                              dashboard_structure_indicator_data[i,]$point_linechart_ind_gdp,
                              dashboard_structure_indicator_data[i,]$graph_title,
                              dashboard_structure_indicator_data[i,]$point_linechart_subtitle,
                              "", TRUE)
  filename <- paste0("ecoin_temp_", i, ".png")
  plotly::save_image(ecoin_fig$fig, filename)
    
  # Assign plot to plots_subpage_env
  assign("filename", filename, plots_subpage_env)
    
  # Knit plot.RMD using the plots_subpage_env and add result to out vector
  plots_out = c(plots_out, knitr::knit_child('plot.RMD', envir = plots_subpage_env))
}
```

`r if (dashboard_structure_indicator_data$point_linechart[1]) {paste(knitr::knit_child(text = plots_out), collapse = '')}`


`r if (dashboard_structure_indicator_data$double_scale[1]) {"## Trend and cycle decomposition"}`

```{r render plots, include=FALSE, eval=dashboard_structure_indicator_data$double_scale[1]}
# Create variable which stores all subpages outputs
plots_out = NULL
  
# Set knitr options to allow duplicate labels (needed for the subpages)
options(knitr.duplicate.label = 'allow')
  
# Create temporary environment which we use for knitting plot.RMD 
plots_subpage_env <- new.env()
for(i in 1:nrow(dashboard_structure_indicator_data)) {
  # Generate the plot and save it as .png file to include it in the report
  double_scale_fig <- generate_chart("double_scale", data, geo_labels,
                                     colors_palette,
                                     dashboard_structure_indicator_data[i,]$double_scale_ind,
                                     dashboard_structure_indicator_data[i,]$double_scale_dim,
                                     dashboard_structure_indicator_data[i,]$graph_title,
                                     dashboard_structure_indicator_data[i,]$double_scale_subtitle,
                                     ".1f", TRUE)
  filename <- paste0("double_scale_temp_", i, ".png")
  plotly::save_image(double_scale_fig$fig, filename)
    
  # Assign plot to plots_subpage_env
  assign("filename", filename, plots_subpage_env)
    
  # Knit plot.RMD using the plots_subpage_env and add result to out vector
  plots_out = c(plots_out, knitr::knit_child('plot.RMD', envir = plots_subpage_env))
}
```

`r if (dashboard_structure_indicator_data$double_scale[1]) {paste(knitr::knit_child(text = plots_out), collapse = '')}`


`r if (dashboard_structure_indicator_data$forecast_chart[1]) {"## Forecasts"}`

```{r render plots, include=FALSE, eval=dashboard_structure_indicator_data$forecast_chart[1]}
# Create variable which stores all subpages outputs
plots_out = NULL
  
# Set knitr options to allow duplicate labels (needed for the subpages)
options(knitr.duplicate.label = 'allow')
  
# Create temporary environment which we use for knitting plot.RMD 
plots_subpage_env <- new.env()
for(i in 1:nrow(dashboard_structure_indicator_data)) {
  if (!is.na(dashboard_structure_indicator_data[i,]$forecast_chart_ind)) {
    # Generate the plot and save it as .png file to include it in the report
    forecast_fig <- generate_chart("forecast", NULL, geo_labels, colors_palette,
                                   dashboard_structure_indicator_data[i,]$forecast_chart_ind,
                                   dashboard_structure_indicator_data[i,]$forecast_chart_xlsx_sheet_name,
                                   dashboard_structure_indicator_data[i,]$graph_title, "", "")
    filename <- paste0("forecast_temp_", i, ".png")
    plotly::save_image(forecast_fig$fig, filename)
    # Assign plot to plots_subpage_env
    assign("filename", filename, plots_subpage_env)
  }
  else {
    # Generate the plot and save it as .png file to include it in the report
    forecast_fig <- generate_chart("forecast", NULL, geo_labels, colors_palette,
                                   dashboard_structure_indicator_data[i,]$forecast_chart_ind,
                                   dashboard_structure_indicator_data[i,]$forecast_chart_xlsx_sheet_name,
                                   dashboard_structure_indicator_data[i,]$graph_title,
                                   "", i, TRUE)
    filename <- paste0("forecast_temp_", i, "_", 1, ".png")
    # Assign plot to plots_subpage_env
    assign("filename", filename, plots_subpage_env)
    
    for (j in seq(3, length(forecast_fig)*2, 2)) {
      name <- paste0("forecast_temp_", i, "_", j, ".png")
      assign(paste0("filename", j), name, plots_subpage_env)
    }
  }
    
  # Knit plot.RMD using the plots_subpage_env and add result to out vector
  plots_out = c(plots_out, knitr::knit_child('plot.RMD', envir = plots_subpage_env))
}
```

`r if (dashboard_structure_indicator_data$forecast_chart[1]) {paste(knitr::knit_child(text = plots_out), collapse = '')}`


`r if (dashboard_structure_indicator_data$map[1]) {"## Map"}`

```{r render plots, include=FALSE, eval=dashboard_structure_indicator_data$map[1]}
# Create variable which stores all subpages outputs
plots_out = NULL
  
# Set knitr options to allow duplicate labels (needed for the subpages)
options(knitr.duplicate.label = 'allow')
  
# Create temporary environment which we use for knitting plot.RMD 
plots_subpage_env <- new.env()
for(i in 1:nrow(dashboard_structure_indicator_data)) {
  # Generate the plot and save it as .png file to include it in the report
  filename <- paste0("map_temp_", i, ".png")
  map <- generate_chart("map", data, geo_labels, NULL,
                        dashboard_structure_indicator_data[i,]$map_ind,
                        filename,
                        dashboard_structure_indicator_data[i,]$graph_title,
                        dashboard_structure_indicator_data[i,]$map_subtitle,
                        dashboard_structure_indicator_data[i,]$map_legend_title,
                        TRUE)
    
  # Assign plot to plots_subpage_env
  assign("filename", filename, plots_subpage_env)
    
  # Knit plot.RMD using the plots_subpage_env and add result to out vector
  plots_out = c(plots_out, knitr::knit_child('plot.RMD', envir = plots_subpage_env))
}
```

`r if (dashboard_structure_indicator_data$map[1]) {paste(knitr::knit_child(text = plots_out), collapse = '')}`
